---
title: "Disfluencies and Deception"
subtitle: "Tallinn University"
author: "Martin Corley"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css:
      - default
      - "../my_lib/hygge-edi.css"
      - "../my_lib/edi-colours.css"
      - "../my_lib/edi-fonts.css"
      - "../my_lib/animate.css"
    lib_dir: libs
    nature:
      beforeInit: "../my_lib/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"

---
# Ground Rules
<br>
- this course is pulled together from several sources
  - slides on gitbub, google slides
  - I'll make sure you have access
- feel free to ask questions at any time
<br>
<br>
<br>

--

.content-box-green[.center[
keep things informal]
]


---
class: edi-softblue, center, middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(knitr.duplicate.label = 'allow')

```

# Plan for the Course
<br>
## 1. What are Disfluencies?
## 2. Disfluencies and Prediction
## 3. What is Deception?
## 4. Disfluencies and Deception

???
- at the moment we don't intend to talk about *speech errors*
- though we could do...
---
class: edi-softblue, center, middle, animated, bounceInDown

# Disfluencies

---
```{r child='disfluencies.Rmd'}
```
---
