---
title: "Presentations"
subtitle: ""  
author: "Martin Corley"
institute: "Department of Psychology<br/>The University of Edinburgh"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: 
      - xaringan-themer.css
      - mc_libs/tweaks.css
    nature:
      beforInit: "mc_libs/macros.js"
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    editor_options:
      chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(htmltools.dir.version = FALSE)
options(digits=4,scipen=2)
options(knitr.table.format="html")
xaringanExtra::use_xaringan_extra(c("tile_view","animate_css","tachyons"))
xaringanExtra::use_extra_styles(
  mute_unhighlighted_code = FALSE
)
library(knitr)
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(
  dev = "svg",
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  fig.showtext = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#5F76B7",
  secondary_color = "#FCBB06",
  inverse_header_color = "#FFFFFF"
)
```

```{r ggtheme,include=FALSE}
# don't ask me why this only works in a different code block
theme_set(theme_xaringan())
```

class: inverse, middle
## 1. what are you going to say?

.pt3[
## 2. what props do you need?
]

.pt3[
## 3. how are you going to say it?
]
???
- by "props", I mean the slides or poster that you might typically use in academia.  I'm going to try and persuade you that they really _are_ props; the "message" should come from you, not from your visual aids

- "how you're going to say it" refers to the act of speaking, in front of an audience which can be anything from one person in front of a poster to a couple of hundred in an auditorium

---
count: false
class: inverse, middle
## 1. .primary[what are you going to say?]


.pt3[
## 2. what props do you need?
]

.pt3[
## 3. how are you going to say it?
]

---
# The 5 Ws

- **What** are you presenting?
  + talk? poster? what is it about?
  
- **Why** are you presenting it?
  + what's its purpose?
  + what do you want people to take home?
--

- **Who** are you presenting to?

- **When** and

- **Where** are you presenting?

---
# What should be in my presentation?

- **Background**
  + just enough to motivate the research problem
  
- **Method**

- **Results** and their interpretation/discussion
  + think about statistics/graphs

- **Summary and Conclusions**
  + the all-important take-home message

---
class: inverse, middle
## 1. what are you going to say?


.pt3[
## 2. .primary[what props do you need?]
]

.pt3[
## 3. how are you going to say it?
]
---
class: inverse, middle
## 1. what are you going to say?


.pt3[
## 2. what props do you need?
]

.pt3[
## 3. .primary[how are you going to say it?]
]
